\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-11-21 Final Paper/PaperJLin.tex
Added Breif Results interpretation and tables with General Trends on DV

\usepackage{fullpage} %full page typesetting
\usepackage{setspace} %allows for non-singlespacing
\usepackage{graphicx} %graphics capabilities
\usepackage{latexsym} %extra symbols
\usepackage{rotating} %rotation for figures
\usepackage{longtable} %tables that fill more than a single page
%\usepackage{hyperref} %hypertext links in the document
\usepackage{natbib} %better bibliographies
\usepackage{authblk} %author and affiliation in opening
\usepackage{mathpazo} %use palatino font, rather than times
\usepackage{appendix}
\usepackage{lscape}
\usepackage{tabulary}
\usepackage[nottoc]{tocbibind}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=cyan]{hyperref}
\usepackage{ifthen}

@@

\begin{table}[h!]
	\centering
	\caption{\tb{Percentage of People in Each Place of Residence by Polity}}
	\begin{tabulary}{\linewidth}{l c c c c}
		\hline
		\tb{Country}&\tb{Rural}&\tb{Small Town}&\tb{Suburban}&\tb{Urban}\\
		\hline
		Worldwide&26.98&22.95&13.37&36.70 \\
		Argentina&-&13.30&-&86.70 \\
		Australia&10.92&18.73&16.98&53.37 \\
		Austria&41.67&27.54&18.19&12.60 \\
		Bulgaria&26.33&20.82&36.14&16.72 \\
		Czech Republic&26.68&39.87&5.01&29.24 \\
		Germany&28.80&42.56&9.53&19.11 \\
		Finland&25.16&23.39&42.50&8.95 \\
		France&35.10&37.34&11.72&15.84 \\
		Great Britain&17.68&52.84&-&29.48 \\
		Greece (2012)&40.77&10.62&11.51&31.10 \\
		Greece (2015)&5.86&21.48&13.99&58.68 \\
		Iceland&9.06&28.87&26.17&35.90 \\
		Ireland&-&40.91&-&59.09 \\
		Israel&20.50&54.40&25.10&- \\
		Japan&12.80&25.86&17.86&43.47 \\
		Kenya&66.67&-&-&33.33 \\
		Latvia (2011)&36.75&18.13&-&45.12 \\
		Latvia (2014)&34.46&25.29&10.42&29.83 \\
		Mexico (2012)&18.33&11.67&-&70.00 \\
		Mexico (2015)&18.38&11.28&-&70.34 \\
		Montenegro&37.47&36.72&12.85&12.96 \\
		Norway&26.43&25.54&13.69&34.35 \\
		New Zealand (2011)&16.32&38.12&-&45.56 \\
		New Zealand (2014)&13.36&21.04&-&65.61 \\
		Peru&20.99&-&-&79.01 \\
		Philippines&45.00&14.58&3.33&37.88 \\
		Poland&35.85&42.57&9.64&11.93 \\
		Portugal&28.75&25.48&16.81&28.95 \\
		Romania (2012)&44.63&22.83&2.37&30.97 \\
		Romania (2015)&41.82&29.95&11.78&16.46 \\
		Serbia&49.62&24.04&9.44&16.90 \\
		Slovakia&42.38&39.16&1.48&16.97 \\
		Slovenia&22.88&12.65&49.66&14.61 \\
		South Africa&30.77&-&-&69.23 \\
		South Korea&17.00&28.40&6.00&48.60 \\
		Sweden&17.55&22.12&21.15&39.18 \\
		Switzerland&26.67&0.66&47.30&25.37 \\
		Turkey&19.06&21.64&17.96&41.34 \\
		\hline
	\end{tabulary} \\
\e{Source:} Comparative Study of Electoral Systems Module IV 
\label{table2}
\end{table}

@@

\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Worldwide}}
	\begin{tabulary}{\linewidth}{l c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Worldwide} \\
		\hline
		Small Town&-.1338***  \\    
		  & (.0336)   \\
		Suburban & -.2591***\\ 
		 & (.0358) \\
		Urban   & -.0482   \\
		  & (.0300)    \\
		Constant   & 5.597***  \\
		&(.0234) \\
		N  & 47,821  \\
		$R^2$	& 0.0011 \\
		\hline                                       
    \end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table3}
\end{table}

@@

\begin{table}
\centering
\def\arraystretch{1.5}
\caption{\tb{Self-Placement Ideology - Central/Latin America}}
	\begin{tabulary}{\linewidth}{l c c c c}
	\\
	\hline
	\tb{Place of Residence}&\tb{Argentina}&\tb{Mexico (2012)}&\tb{Mexico (2015)} &\tb{Peru}\\
	\hline
	Small Town  & -    & .6408***   &-.4734    & -   \\      
	  & -  & (.2394) & (.3113)    & -    \\
	Suburban    & -    & -   & -   & -    \\ 
	& -     & -    & -   & -    \\
	Urban   & -.9521*** & -.1417   & -.4084*   & .0883  \\
	   & (.2150)   &(.1678)   & (.2210)  & (.1743)      \\
	Constant   & 6.495*** & 6.6516*** & 6.1690*** & 6.646***   \\
	&(.2046)&(.1493)&(.1998)&(.1564) \\
	N  & 1,241 &1,812   & 910 & 1,438   \\
	$R^2$ & 0.0156   &0.0082   &0.0041 &0.0002     \\
	\hline                                       
	\end{tabulary} 
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table4}
\end{table}

@@

\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Scandinavia}}
	\begin{tabulary}{\linewidth}{l c c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Finland}&\tb{Iceland}&\tb{Norway}&\tb{Sweden} \\
		\hline
		Small Town&.1418&.5194**&.0568&-.1030 \\
		&(.1646)&(.2279)&(.1534)&(.2644) \\
		Suburban&-.0612&.7355***&-.0277&.0794 \\
		&(.1452)&(.2290)&(.1847)&(.2690) \\
		Urban&-.7128***&.3840*& .0888&-.1723\\
		&(.2202)&(.2220)&(.1429)&(.2368) \\
		Constant&5.6503***&4.990***&5.5985***&5.2230*** \\
		&(.1169)&(.2006)&(.1080)&(.1973) \\
		N&1,387&1,266&1,618&792\\
		$R^2$&0.0111&0.0096&0.0004&0.0018 \\
		\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table6}
\end{table}

@@

\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Central Europe}}
	\begin{tabulary}{\linewidth}{l c c c c c}
		\\
		\hline
		\tb{Place of Residence} &\tb{Austria}&\tb{Czech Republic}& \tb{Poland} &\tb{Slovakia}&\tb{Slovenia} \\
		\hline
		Small Town&-.2108& -.0223 & .0829 & .4318*** & .0229 \\
		&(.1540) & (.1687) & (.1421) & (.2000) & (.3262)\\
		Suburban&-.1433& -.6091*& -.1414 & 1.059& .1549** \\
		&(.1570)&(.3281) & (.2210) & (.6711) & (.2491)\\
		Urban&-.3005**&.2860 & -.2002 & .8061*** & -1.3416***\\
		&(.1335) &(.1773) & (.2042) & (.2437) & (.3169)\\
		Constant& 5.3726***& 4.9135***& 6.015*** & 4.7527***  & 4.6780 ***\\
		&(.1219) & (.1300) & (.1050) & (.1370) & (.2060)\\
		N&3,363& 1,412& 1,634 & 879& 666 \\
		$R^2$&0.0018&0.0065 & 0.0016 & 0.0148 & 0.0629\\
		\hline
		\end{tabulary}
	\\
	\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
	\e{Reference:} A rural place of residence serves as the baseline for comparison
	\label{table7}
	\end{table}

@@

\begin{table}
\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Eastern Europe}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Latvia (2011)} &\tb{Latvia (2014)} \\
		\hline
		Small Town &.1635 &.0560 \\
		&(.2433) & (.2224) \\
		Suburban&- & -.1285 \\
		& - & (.2893) \\
		Urban&-.2292&.0221 \\
		& (.1850) & (.1996) \\
		Constant & 6.2775*** &6.3285*** \\
		& (.1360) & (.1396) \\
		N&787 & 815\\
		$R^2$& 0.0041 &0.0005 \\
		\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table9}
\end{table}

\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Middle East}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Israel} & \tb{Turkey} \\
		\hline
		Small Town&1.2822*** & .0228 \\
		&(.2427)  & (.3120)\\
		Suburban&1.5019*** &.5457 \\
		& (.2767)  & (.3326 )\\
		Urban &- & .2337\\
		&- & (.2764)\\
		Constant& 4.9193*** &5.7434*** \\
		& (,.2067)  & (.2268)\\
		N&912 & 965\\
		$R^2$&0.0371 & 0.0037 \\
		\hline 
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table10}
\end{table}

\begin{table}
	\centering
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Africa}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Kenya}& \tb{South Africa} \\
		\hline
		Small Town&- &-\\
		&- & -\\
		Suburban&- & -\\
		& - &- \\
		Urban&-1.2690*** &-.06719 \\
		&(.3701)  &(.1664)\\
		Constant&6.7690*** &6.4965*** \\
		& (.1932) & (.1392) \\
		N&506 & 967\\
		$R^2$&0.0228 &0.0002 \\
		\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table11}
\end{table}

\begin{table}
	\centering 
	\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Asia}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Place of Residence} & \tb{Japan} & \tb{South Korea}\\
	\hline
	Small Town &.1898 & -.0347 \\
	&(.1463) & (.2738 )\\
	Suburban&.1717 & -.1176 \\
	& (.1574) & (.4343 )\\
	Urban & .2429* &.3140 \\
	& (.1365) & (.2518)\\
	Constant& 5.4179*** & 5.264*** \\
	& (.1210) & (.2158)\\
	N&1,563 & 717\\
	$R^2$& 0.0020 & 0.0052\\
	\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table12}
\end{table}

@@

@@

@@

@@

\begin{table}
	\centering
	\caption{\tb{Regimes by Level of Democracy, Regime Age, and Electoral Formula}}
	\begin{tabulary}{\linewidth}{l c c c}
		\hline
		\tb{Country} & \tb{Level of Democracy} & \tb{Age of Regime} & \tb{Electoral Formula} \\
		\hline
		Argentina&9&32&Proportional \\
		Australia& 10&112&Majoritarian \\
		Austria&9&24&Proportional\\
		Bulgaria&8&24&Proportional\\
		Czech Republic&9&20&Proportional \\
		Finland&10&71& Proportional \\
		France&9&43&Majoritarian \\
		Germany&10&23&Mixed \\
		Great Britain&10&135&Majoritarian \\
		Greece (2015)&10&40&Proportional \\
		Ireland&10&90&Proportional \\
		Israel&10&60&Proportional \\
		Japan&10&61&Mixed\\
		Kenya&9&11&Majoritarian \\
		Latvia (2014)&8&23&Proportional\\
		Mexico (2015)& 8&18&Mixed\\
		Montenegro&9&6&Proportional\\
		Norway&10&68&Proportional\\
		New Zealand (2014)& 10& 137& Mixed\\
		Peru&9&15&Proportional\\
		Philippines&8&26&Majoritarian\\
		Poland&10&20&Proportional\\
		Portugal&10&39&Proportional\\
		Romania (2014) &9&18& Mixed \\
		Serbia& 8&6&Proportional\\
		Slovakia&10&23&Proportional\\
		Slovenia&10&20&Proportional\\
		South Africa&9&20& Proportional \\
		South Korea&8&24&Mixed\\
		Sweden&10&97&Proportional\\ 
		Switzerland&10&163&Proportional\\
		Turkey&3&32&Proportional\\
		United States&10&203&Majoritarian \\
		\hline
	\end{tabulary}
\\
\e{Source:} Polity IV Project and CSES Macro Report
\label{table101}
\end{table}

@@

>>>>

\usepackage{fullpage} %full page typesetting
\usepackage{setspace} %allows for non-singlespacing
\usepackage{graphicx} %graphics capabilities
\usepackage{latexsym} %extra symbols
\usepackage{rotating} %rotation for figures
\usepackage{longtable} %tables that fill more than a single page
%\usepackage{hyperref} %hypertext links in the document
\usepackage{natbib} %better bibliographies
\usepackage{authblk} %author and affiliation in opening
\usepackage{mathpazo} %use palatino font, rather than times
\usepackage{appendix}
\usepackage{lscape}
\usepackage{tabulary}
\usepackage[nottoc]{tocbibind}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=cyan]{hyperref}
\usepackage{ifthen}
\usepackage{float}

@@

\begin{table}
	\centering
	\caption{\tb{Percentage of People in Each Place of Residence by Polity}}
	\begin{tabulary}{\linewidth}{l c c c c}
		\hline
		\tb{Country}&\tb{Rural}&\tb{Small Town}&\tb{Suburban}&\tb{Urban}\\
		\hline
		Worldwide&26.98&22.95&13.37&36.70 \\
		Argentina&-&13.30&-&86.70 \\
		Australia&10.92&18.73&16.98&53.37 \\
		Austria&41.67&27.54&18.19&12.60 \\
		Bulgaria&26.33&20.82&36.14&16.72 \\
		Czech Republic&26.68&39.87&5.01&29.24 \\
		Germany&28.80&42.56&9.53&19.11 \\
		Finland&25.16&23.39&42.50&8.95 \\
		France&35.10&37.34&11.72&15.84 \\
		Great Britain&17.68&52.84&-&29.48 \\
		Greece (2012)&40.77&10.62&11.51&31.10 \\
		Greece (2015)&5.86&21.48&13.99&58.68 \\
		Iceland&9.06&28.87&26.17&35.90 \\
		Ireland&-&40.91&-&59.09 \\
		Israel&20.50&54.40&25.10&- \\
		Japan&12.80&25.86&17.86&43.47 \\
		Kenya&66.67&-&-&33.33 \\
		Latvia (2011)&36.75&18.13&-&45.12 \\
		Latvia (2014)&34.46&25.29&10.42&29.83 \\
		Mexico (2012)&18.33&11.67&-&70.00 \\
		Mexico (2015)&18.38&11.28&-&70.34 \\
		Montenegro&37.47&36.72&12.85&12.96 \\
		Norway&26.43&25.54&13.69&34.35 \\
		New Zealand (2011)&16.32&38.12&-&45.56 \\
		New Zealand (2014)&13.36&21.04&-&65.61 \\
		Peru&20.99&-&-&79.01 \\
		Philippines&45.00&14.58&3.33&37.88 \\
		Poland&35.85&42.57&9.64&11.93 \\
		Portugal&28.75&25.48&16.81&28.95 \\
		Romania (2012)&44.63&22.83&2.37&30.97 \\
		Romania (2015)&41.82&29.95&11.78&16.46 \\
		Serbia&49.62&24.04&9.44&16.90 \\
		Slovakia&42.38&39.16&1.48&16.97 \\
		Slovenia&22.88&12.65&49.66&14.61 \\
		South Africa&30.77&-&-&69.23 \\
		South Korea&17.00&28.40&6.00&48.60 \\
		Sweden&17.55&22.12&21.15&39.18 \\
		Switzerland&26.67&0.66&47.30&25.37 \\
		Turkey&19.06&21.64&17.96&41.34 \\
		\hline
	\end{tabulary} \\
\e{Source:} Comparative Study of Electoral Systems Module IV 
\label{table2}
\end{table}

@@

\begin{table}[H]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Worldwide}}
	\begin{tabulary}{\linewidth}{l c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Worldwide} \\
		\hline
		Small Town&-.1338***  \\    
		  & (.0336)   \\
		Suburban & -.2591***\\ 
		 & (.0358) \\
		Urban   & -.0482   \\
		  & (.0300)    \\
		Constant   & 5.597***  \\
		&(.0234) \\
		N  & 47,821  \\
		$R^2$	& 0.0011 \\
		\hline                                       
    \end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table3}
\end{table}

@@

\begin{table}[H]
\centering
%\def\arraystretch{1.5}
\caption{\tb{Self-Placement Ideology - Central/Latin America}}
	\begin{tabulary}{\linewidth}{l c c c c}
	\\
	\hline
	\tb{Place of Residence}&\tb{Argentina}&\tb{Mexico (2012)}&\tb{Mexico (2015)} &\tb{Peru}\\
	\hline
	Small Town  & -    & .6408***   &-.4734    & -   \\      
	  & -  & (.2394) & (.3113)    & -    \\
	Suburban    & -    & -   & -   & -    \\ 
	& -     & -    & -   & -    \\
	Urban   & -.9521*** & -.1417   & -.4084*   & .0883  \\
	   & (.2150)   &(.1678)   & (.2210)  & (.1743)      \\
	Constant   & 6.495*** & 6.6516*** & 6.1690*** & 6.646***   \\
	&(.2046)&(.1493)&(.1998)&(.1564) \\
	N  & 1,241 &1,812   & 910 & 1,438   \\
	$R^2$ & 0.0156   &0.0082   &0.0041 &0.0002     \\
	\hline                                       
	\end{tabulary} 
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table4}
\end{table}

@@

\begin{table}[H]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Scandinavia}}
	\begin{tabulary}{\linewidth}{l c c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Finland}&\tb{Iceland}&\tb{Norway}&\tb{Sweden} \\
		\hline
		Small Town&.1418&.5194**&.0568&-.1030 \\
		&(.1646)&(.2279)&(.1534)&(.2644) \\
		Suburban&-.0612&.7355***&-.0277&.0794 \\
		&(.1452)&(.2290)&(.1847)&(.2690) \\
		Urban&-.7128***&.3840*& .0888&-.1723\\
		&(.2202)&(.2220)&(.1429)&(.2368) \\
		Constant&5.6503***&4.990***&5.5985***&5.2230*** \\
		&(.1169)&(.2006)&(.1080)&(.1973) \\
		N&1,387&1,266&1,618&792\\
		$R^2$&0.0111&0.0096&0.0004&0.0018 \\
		\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table6}
\end{table}

@@

\begin{table}[H]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Central Europe}}
	\begin{tabulary}{\linewidth}{l c c c c c}
		\\
		\hline
		\tb{Place of Residence} &\tb{Austria}&\tb{Czech Republic}& \tb{Poland} &\tb{Slovakia}&\tb{Slovenia} \\
		\hline
		Small Town&-.2108& -.0223 & .0829 & .4318*** & .0229 \\
		&(.1540) & (.1687) & (.1421) & (.2000) & (.3262)\\
		Suburban&-.1433& -.6091*& -.1414 & 1.059& .1549** \\
		&(.1570)&(.3281) & (.2210) & (.6711) & (.2491)\\
		Urban&-.3005**&.2860 & -.2002 & .8061*** & -1.3416***\\
		&(.1335) &(.1773) & (.2042) & (.2437) & (.3169)\\
		Constant& 5.3726***& 4.9135***& 6.015*** & 4.7527***  & 4.6780 ***\\
		&(.1219) & (.1300) & (.1050) & (.1370) & (.2060)\\
		N&3,363& 1,412& 1,634 & 879& 666 \\
		$R^2$&0.0018&0.0065 & 0.0016 & 0.0148 & 0.0629\\
		\hline
		\end{tabulary}
	\\
	\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
	\e{Reference:} A rural place of residence serves as the baseline for comparison
	\label{table7}
	\end{table}

@@

\begin{table}[H]
\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Eastern Europe}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Latvia (2011)} &\tb{Latvia (2014)} \\
		\hline
		Small Town &.1635 &.0560 \\
		&(.2433) & (.2224) \\
		Suburban&- & -.1285 \\
		& - & (.2893) \\
		Urban&-.2292&.0221 \\
		& (.1850) & (.1996) \\
		Constant & 6.2775*** &6.3285*** \\
		& (.1360) & (.1396) \\
		N&787 & 815\\
		$R^2$& 0.0041 &0.0005 \\
		\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table9}
\end{table}

For the data that is available to the Middle East, Africa and Asia, there are simply not enough cases here to make general arguments about the region as a whole. Nonetheless, they are still useful in helping us to understand which countries have a sharper urban-rural divide.

To start, Table \ref{table10} highlights Israel as a country in the Middle East with sharp urban and suburban divides to the rural areas of the country in terms of its political ideology. This is not an effect that is seen in Turkey. A reason for this trend is the freedoms that the people in these countries experience. While it is hard to tell if this pattern is true for all countries in the region, it is worth noting that the differences in the level of democracy here may have a great influence in individual political attitudes. Like the actors in Western Europe and much of the western, democratized world, Israel stands as one of the freest nations in the region. Their democracy has been established for 60 years at the time of this election. Meanwhile, Turkey is the least free of all of the countries that are surveyed in this Module. This limit in freedom of speech at the ballot box may also lay to limit freedom of association and expression for the people in the country, limiting the influence of one's vicinity and social group influence on one's political attitudes.

\begin{table}[H]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Middle East}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Israel} & \tb{Turkey} \\
		\hline
		Small Town&1.2822*** & .0228 \\
		&(.2427)  & (.3120)\\
		Suburban&1.5019*** &.5457 \\
		& (.2767)  & (.3326 )\\
		Urban &- & .2337\\
		&- & (.2764)\\
		Constant& 4.9193*** &5.7434*** \\
		& (,.2067)  & (.2268)\\
		N&912 & 965\\
		$R^2$&0.0371 & 0.0037 \\
		\hline 
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table10}
\end{table}

In the wake of the decolonization movement, countries in Africa are rather young in terms of the length of time that their democracy has been in place. In both of the cases displayed in Table \ref{table11}, it does not seem that the age of the democracy is the reason that place is likely to influence political ideology like other regions in the world. Kenya, a younger regime than South Africa, has a greater difference between urban and rural residents such that urban residents are more likely to be left-leaning at a larger factor (1.269 points on average to the left) than in other places in the world.

\begin{table}[H]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Africa}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Kenya}& \tb{South Africa} \\
		\hline
		Small Town&- &-\\
		&- & -\\
		Suburban&- & -\\
		& - &- \\
		Urban&-1.2690*** &-.06719 \\
		&(.3701)  &(.1664)\\
		Constant&6.7690*** &6.4965*** \\
		& (.1932) & (.1392) \\
		N&506 & 967\\
		$R^2$&0.0228 &0.0002 \\
		\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table11}
\end{table}

In this sample of countries from Asia, the data in Table \ref{table12}, suggests that neither Japan nor South Korea exhibit a significant trends towards having place influence a person's placement on the left-right scale. This is also visible in countries in the Pacific Island, and Australia. But in the cases of the countries displayed in table \ref{table13}, the more democratic a place is does not necessarily suggest that there is a greater division between urban and rural residents in terms of their political ideologies. The Philippines, for instance, is less free than Australia and New Zealand, but demonstrate a greater place divide in terms of political ideology.

\begin{table}[H]
	\centering 
	%\def\arraystretch{1.5}
	\caption{\tb{Self-Placement Ideology - Asia}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Place of Residence} & \tb{Japan} & \tb{South Korea}\\
	\hline
	Small Town &.1898 & -.0347 \\
	&(.1463) & (.2738 )\\
	Suburban&.1717 & -.1176 \\
	& (.1574) & (.4343 )\\
	Urban & .2429* &.3140 \\
	& (.1365) & (.2518)\\
	Constant& 5.4179*** & 5.264*** \\
	& (.1210) & (.2158)\\
	N&1,563 & 717\\
	$R^2$& 0.0020 & 0.0052\\
	\hline
	\end{tabulary}
\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table12}
\end{table}

@@

\subsubsection{Summary: Place Matters?}

In our analysis for the influence of place of residence on the political attitudes of individuals in certain countries of the world, we generate rather mixed conclusions based on the data. When we consider the differences between neighboring countries in terms of differences in regime age and level of democracy, these factors, nonetheless produce mixed results as an answer to the question about whether place matters in influencing political ideology. From the overall trends, we have evidence to suggest that place of residence does matter, but it depends on contextual factors that extend beyond the information that a country's regime stability, as determined by age, and the freedoms people enjoy, as determined by level of democracy, can tell us about the underpinnings of these observations.

@@

In the previous section, I looked at specific countries to try to discern the extent to which place matters in a person's self placement on the political ideology spectrum. From the results of that model, we can see that place matters, but the country to which the place is embedded in also matters to determine and influence the relationship between the variables. In this section, I aim to explore a more objective variable on liberalism to see the extent to which place really matters in influencing individual political attitudes towards economic and social inequality. As previous research suggests (notably, \cite{walsh_putting_2012}), residents of rural environments tend to be more conservative when it comes to social spending, even if the results will work in their favor.

The analysis employed in this section will look at general trends to see if there is indeed an influence between place and positions on spending. A variable was created for this analysis which aggregates the views that people have for spending government money on various social services in the country (see Appendix \ref{AppendixB} for more information on variable coding).

\begin{table}[H]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Issue Stances - General Trends}}
	\begin{tabulary}{\linewidth}{l c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Worldwide} \\
		\hline 
		Small Town&-.1005*** \\
		&(.0136)\\
		Suburban&-.1737***\\
		&(.0162) \\
		Urban&-.1306*** \\
		&(.0123)\\
		Constant&5.7164*** \\
		&(.0093) \\
		N&42,500 \\
		$R^2$&0.0037 \\
		\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table14}
\end{table}

From the results that reflects general trends in the world based on the new liberalism variable, we see that there are some differences between place of residence and issue stances. Looking at Table \ref{table14} alongside the earlier Table \ref{table3}, we see that there urban-rural divide is more pronounced than it was before. (Both Tables are reproduced in Appendix \ref{AppendixD} for simplicity in comparison)

@@

In the analysis of results for self-placement ideology, we considered if a country's macro variables has any influence on the relationship between place of residence and political ideology.

To test the core of Hypothesis 3, we will turn next to how these macro variables influence the context where each respondent casts their ballot. I will analyze the big picture before diving into the specifics regarding each factor. Therefore, we will look at the \e{Polity Difference} hypothesis before diving into \e{Level of Democracy}, \e{Regime Age}, and \e{Electoral Formula} hypotheses.

Table \ref{table15} shows the influence of each of the macro variables, when taken together, on the relationship between place of residence and individual placement on political ideology and on the objective measures seen in the liberalism measure.

\begin{table}[H]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{All Macro Variables - General Trends}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Variable}&\tb{Self-Placement}&\tb{Liberalism} \\
	\hline
	\e{Place of Residence} & & \\
	Small Town &-.1000***&-.0018 \\
	&(.0339)&(.0130) \\
	Suburban& -.1517***& .0147 \\
	&(.0401)& (.0157) \\
	Urban&-.0517* & -.0420*** \\
	&(.0304) & (.0117) \\
	\e{Democracy}& -.1995*** & -.0421***\\
	&(.0110) & (.0040)\\
	\e(Regime Age) & -.0014*** &  -.0075***\\
	&(.0002) & (.0001)\\
	\e{Electoral Formula}&.0778*** & -.0440***\\
	&(.0189) & (.0070) \\
	\hline
	Constant& 7.3627*** & 6.5149*** \\
	&(.1067) & (.0391)\\
	N&46,555 & 41,373 \\
	$R^2$&0.0135& 0.1273 \\
	\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table15}
\end{table}

For the purposes of simplicity in the forthcoming discussion, I will analyze the influence of both dependent variables, but primarily focusing on the self-placement of individuals on the ideology spectrum. From the previous discussion in this section, we can see that the major difference between the different places lie primarily in the self-placement score rather than the liberalism variable. While the objective score is interesting in its own ways, and it will be considered, the weight will be placed on how people see themselves and their place on the political spectrum.

@@

\begin{table} [h!]
	\centering
	\caption{\tb{Regimes by Level of Democracy, Regime Age, and Electoral Formula}}
	\begin{tabulary}{\linewidth}{l c c c}
		\hline
		\tb{Country} & \tb{Level of Democracy} & \tb{Age of Regime} & \tb{Electoral Formula} \\
		\hline
		Argentina&9&32&Proportional \\
		Australia& 10&112&Majoritarian \\
		Austria&9&24&Proportional\\
		Bulgaria&8&24&Proportional\\
		Czech Republic&9&20&Proportional \\
		Finland&10&71& Proportional \\
		France&9&43&Majoritarian \\
		Germany&10&23&Mixed \\
		Great Britain&10&135&Majoritarian \\
		Greece (2015)&10&40&Proportional \\
		Ireland&10&90&Proportional \\
		Israel&10&60&Proportional \\
		Japan&10&61&Mixed\\
		Kenya&9&11&Majoritarian \\
		Latvia (2014)&8&23&Proportional\\
		Mexico (2015)& 8&18&Mixed\\
		Montenegro&9&6&Proportional\\
		Norway&10&68&Proportional\\
		New Zealand (2014)& 10& 137& Mixed\\
		Peru&9&15&Proportional\\
		Philippines&8&26&Majoritarian\\
		Poland&10&20&Proportional\\
		Portugal&10&39&Proportional\\
		Romania (2014) &9&18& Mixed \\
		Serbia& 8&6&Proportional\\
		Slovakia&10&23&Proportional\\
		Slovenia&10&20&Proportional\\
		South Africa&9&20& Proportional \\
		South Korea&8&24&Mixed\\
		Sweden&10&97&Proportional\\ 
		Switzerland&10&163&Proportional\\
		Turkey&3&32&Proportional\\
		United States&10&203&Majoritarian \\
		\hline
	\end{tabulary}
\\
\e{Source:} Polity IV Project and CSES Macro Report
\label{table101}
\end{table}

@@

\subsection{Variable Selection}

The CSES provides several issue stance items that reflect how individuals feel toward political parties and policies. The variables described in Table \ref{table100} show the variables that were selected as part of the liberalism scale because it reflects rather universal issues that are at the core of what citizens in each country would have to decide on in terms of the way they see their government spending their tax dollars. Additionally, each of these variables are focused on identifying how individuals feel about certain social issues based on their level of comfort in allocating money to the particular cause. As a results, we can see ther interaction of economic and social policy attitudes at work and see how they interact with place to build a person's ideology.

\subsection{Variable Coding}

The CSES codes the public expenditure variables (D3001) as follows:

\begin{quote}

	1. Much more than now \\ 
	2. Somewhat more than now \\
	3. The same as now \\ 
	4. Somewhat less than now \\
	5. Much less than now \\
	7. Volunteered: Refused \\
	8. Volunteered: Don't Know \\
	9. Missing

\end{quote}
